Summary of "Inferring Method Specifications from Natural Language API Descriptions''

### 2013-02-05 P2-revised-summary/summary.tex
initial version from the exercise

\title{summary}
\author{Dejun Qian\\electronseu@gmail.com}

@@

% the problem solved, the approach used, and the results
This paper \cite{bib:Pandita} addresses the problem of automating the verification process of software product based on the Application Programming Interface (API) documents written in natural language.
Software reuse gives software developers the ability to build larger software products with higher quality in shorter time.
The reused software library is usually provided to the developers in the forms of source code or binary executable,
along with the document explaining to how to use itself.
Reading and understanding the document is important, 
or even the only way when no source code is provided,
to correctly use the provided functionalities.
However, the developers are easily overlook some documents,
and misuse some of the functions,
which will leads to potential inconsistency between the software product and the documents.
Many verification tools are developed to detect the inconsistence,
however these tools only accept formal specifications as their input.
They can't understand documents written in natural language.
This paper presents an approach to fill the gap between what is needed by the existing verification tools and what the document can provide.

>>>>

\title{Summary of "Inferring Method Specifications from Natural Language API Descriptions''}
\author{Dejun Qian\\electronseu@gmail.com}

@@

% the problem solved, the approach used, and the results
Pandita et al. \cite{bib:Pandita} address the problem of automating the verification process of software product based on the Application Programming Interface (API) documents written in natural language.
Software reuse gives software developers the ability to build larger software products with higher quality in shorter time.
The reused software library is usually provided to the developers in the forms of source code or binary executable,
along with the document explaining to how to use itself.
Reading and understanding the document is important, 
or even the only way when no source code is provided,
to correctly use the provided functionalities.
However, the developers are easily overlook some documents,
and misuse some of the functions,
which will leads to potential inconsistency between the software product and the documents.
Many verification tools are developed to detect the inconsistence,
however these tools only accept formal specifications as their input.
They can't understand documents written in natural language.
This paper presents an approach to fill the gap between what is needed by the existing verification tools and what the document can provide.
